Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-11 Grassmannian_cells.tex
added some says, minor changes

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are short exact sequences without any preinjective direct summands.
      %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
      %This is because $\Sigma_2 S_2=0$.
  \end{enumerate}
\end{remark}
We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $\alpha$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
   % \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(d(m,r))=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(1,l)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ is given by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^m$ exactly when $\rk(M_X)\leq l-m$.

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{lemma}
\begin{proof}
  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$. } Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{proof}

@@

\begin{corollary}
    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

@@

\begin{lemma}
  \label{le:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
\end{lemma}
\begin{proof}
  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
\end{proof}
\begin{remark}
  The set $Gr(H_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
\end{remark}

@@

Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
Combining with Lemma~\ref{le:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
The next observation is essential for the results to follow.
\begin{proposition}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
\end{proposition}
\begin{proof}
  \sayD{Proof needed}
  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
  Indeed, we have
  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
\end{proof}

@@

\begin{corollary}
  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
\end{corollary}

@@

\begin{lemma}
  For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
\end{lemma}

@@

\begin{remark}
  \mbox{}
  \begin{enumerate}
    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_Q$ on $\rep\widetilde{K(n)}$. 
      %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
    \item We have 
      $$\tilde P_{2l-1,i}:=\alpha_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=\alpha_i^{-1}.\tilde P_{2l}$$
      for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).

      Now every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. 
    \item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
\end{enumerate}
\end{remark}
Let
$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows.

@@

\begin{align*}
  \xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\(2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n}}[rrd] &&\vdots\\&&(1,\alpha_n)}
\end{align*}
The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $\alpha_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $\alpha_{j_1},\ldots,\alpha_{j_l}$.

>>>>

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}\label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are short exact sequences without any preinjective direct summands.
      %Without the assumption on the direct summands, it is not clear that short exact sequences are preserved.
      %This is because $\Sigma_2 S_2=0$.
  \end{enumerate}
\end{remark}
We will see that the indecomposable representations of dimension $d(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
For a dimension vector $d\in\NN^{Q_0}$, write $R_d(K(n))$ for the affine space of representations of dimension $\alpha$.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
    \item The set of indecomposable representations of dimension $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
   % \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and as we have $\Sigma_2(d(m,r))=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(1,l)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ is given by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^m$ exactly when $\rk(M_X)\leq l-m$.

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{lemma}
\begin{proof}
  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{The proof as written seems to be false as $\Hom(X,P_\ell)\ne0$ does not imply $\Hom(Y,P_\ell)\neq 0$ for all direct summands $Y$ of $X$. The easiest way would be to reorganize 3.8-3.10 in such way that we can assume that $X=P_m^V$ is indecomposable.} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{proof}

@@

\begin{corollary}\sayT{exchange $W$ and $V$?}
    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}

@@

\begin{lemma}
  \label{le:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
\end{lemma}
\begin{proof}
  Define a map $H_m^*\to H_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
  Then $\bar{\varphi}=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.\sayT{why does this imply that $\iota_{m-1}=0$? This should contradict the fact that \eqref{eq:AR sequence} is an AR-sequence.}
  Thus the map $H_m^*\to H_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
\end{proof}
\begin{remark}
  The set $Gr(H_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.\sayT{more details?}
\end{remark}

@@

Following Remark~\ref{rem:reflection recursion}, the reflection functor $\Sigma_1$ provides a natural identification of $H_m$ with $H_{m-1}$ for $m\ge2$. 
Combining with Lemma~\ref{le:preprojective homomorphism duality} we obtain a natural isomorphism $H_m^*\cong H_m$ for $m\ge2$.
The next observation is essential for the results to follow.
\begin{proposition}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\bar{\bar{V}}=\tau V$.
\end{proposition}
\begin{proof}
  \sayD{Proof needed}\sayT{explain $\tau V$. Do we need this?}
  We show that $\bar{\bar{\varphi}}=\tau\varphi$ for $\varphi\in H_m$.
  Indeed, we have
  \[\bar{\bar{\varphi}}=(id\overline{\otimes}\bar{\varphi})\circ\iota_{m-2}=\Big(id\overline{\otimes}\big((id\overline{\otimes}\varphi)\circ\iota_{m-1}\big)\Big)\circ\iota_{m-2}.\]
\end{proof}

@@

\begin{corollary}\sayT{proof?}
  For $V,W\in Gr(H_m)$, $m\ge3$, the space $\Ext(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})$ has dimension 0 or 1.. .
\end{corollary}

@@

\begin{lemma}\sayT{proof? Special case of 3.23?}
  For $V,W\in Gr(H_m)$, $m\ge2$, with $\dim W=1$, we have $\Hom(P_{m+1}^V,P_{m-1}^{\bar{\bar{W}}})\cong\big(H_m/(V+W)\big)^*$.
\end{lemma}

@@

\begin{remark}
  \mbox{}
  \begin{enumerate}
    \item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_Q$ on $\rep\widetilde{K(n)}$. 
      %Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
    \item  Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. 	
		We have 
      $$\tilde P_{2l-1,i}:=\alpha_i.\tilde P_{2l-1},\quad \tilde P_{2l,i}:=\alpha_i^{-1}.\tilde P_{2l}$$
      for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}).

    \item Note that, the dimension vector of $\tilde P_m$ are symmetric. They all have the same middle vertex $(1,1)$ if $m$ is odd and $(2,1)$ if $m$ is even.
\end{enumerate}
\end{remark}
Let
$$I^n_l:=\{(j_1,\ldots,j_{l})\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows.

@@

\begin{align*}
  \xymatrix@R10pt@C20pt{&&(1,\alpha_1)\\(2,1)\ar^{\alpha_1}[rru]\ar^{\alpha_{n}}[rrd] &&\vdots\\&&(1,\alpha_n)}
\end{align*}
The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$, can be obtained from this quiver by erasing the arrow $\alpha_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $\alpha_{j_1},\ldots,\alpha_{j_l}$ and the corresponding sinks.
